---
title: "North_Carolina_Data"
author: "Tate Green"
date: "4/8/2019"
output: html_document
---

```{r, echo=FALSE, include = FALSE}
library(readr)
library(tidyverse)
library(gt)
library(dplyr)

orig <- read_csv(
  "ps_4_elections-poll-nc09-3.csv",
                 col_types = cols(
                   .default = col_character(),
                   turnout_scale = col_double(),
                   turnout_score = col_double(),
                   w_LV = col_double(),
                   w_RV = col_double(),
                   final_weight = col_double(),
                   timestamp = col_datetime(format = "")))

```



```{r, echo=FALSE}
dem <- orig %>%
  count(response) %>%
  filter(response == "Dem")
## Filter to get only those who responded as a Democrat 
```

```{r, echo=FALSE}
diff <- orig %>%
  count(response) %>%
  spread(response, n) %>%
  mutate(rep_und = Rep - Und)
## We used spread to spread out the data and make it easy to select
## We mutate the data to subtract Rep from Und
```

```{r, echo=FALSE}
diffval <- orig %>%
  filter(gender != gender_combined) %>%
  nrow()
## We use the "!" function to filter out the gender_combined
```


```{r, echo=FALSE}
white <- orig %>%
  filter(race_eth == "White") %>%
  filter(file_race_black != "White") %>%
  nrow()
## We use the "!" function to filter out the White respondents 
## We filter race_eth so that we are only looking at those categorized as "White"
```

```{r, echo=FALSE}
rep_time <- orig %>% 
  filter(response == "Rep") %>%
  select(timestamp) %>%
  arrange(timestamp) %>%
  slice(1)

## We use slice in order to get the first response only from the Republicans

dem_time <- orig %>%
  filter(response == "Dem") %>%
  select(timestamp) %>%
  arrange(timestamp) %>%
  slice(1)

## We use slice in order to get the first response only from the Democrats

time_difference <- as.numeric(rep_time - dem_time)

## We then subtract the time of the first republican respondent and the time of the first democrat respondent t get the minutes difference. 
```

There were `r dem$n[1]` respondents who supported the Democratic candidate.

There were `r diff$rep_und[1]` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r diffval` individuals for whom these variables have different values.

There are `r white` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r round(time_difference)`  minutes (rounded to the nearest minute) before the first response of Dem.

```{r, echo=FALSE}
library(readr)
library(tidyverse)
library(gt)
library(dplyr)
library(ggplot2)

## We download the gt package to use functions later that will help us label our plots easily and efficently 

orig <- read_csv(
  "ps_4_elections-poll-nc09-3.csv",
                 col_types = cols(
                   .default = col_character(),
                   turnout_scale = col_double(),
                   turnout_score = col_double(),
                   w_LV = col_double(),
                   w_RV = col_double(),
                   final_weight = col_double(),
                   timestamp = col_datetime(format = "")))
## We used these functions to remove error from our dataset
```

```{r make_chart, echo=FALSE, results="asis"}
orig %>%
  select(final_weight, response, race_eth) %>%
  mutate(race_eth = fct_relevel(race_eth, c("White", "Black", "Hispanic", "Asian", "Other"))) %>%
  group_by(race_eth, response) %>%
  summarize(total = sum(final_weight)) %>%
  filter(race_eth != "[DO NOT READ] Don't know/Refused") %>%
  ## We filter out those who either refused to record or didn't know their
  ## ethnicity 
  spread(key = response, value = total, fill = 0) %>%
  ungroup() %>%
  mutate(all = Dem + Rep + Und + `3`) %>%
  mutate(Dem = Dem / all) %>% 
  mutate(Rep = Rep / all) %>%
  mutate(Und = Und / all) %>%
  ## We use the mutate function in order to find the correct proportions of 
  ## respondents and their political party
  select(-all, -`3`) %>%
  na_if(0) %>%
  gt() %>%
  ## we use the gt function here to label our plot
  ## we use the na_if function to remove the na and replace it with 0
    tab_header(
      title = "Polling Results in North Carolina 9th Congressional District") %>%
    tab_source_note(
      source_note = "Source: New York Times Upshot/Siena Data") %>%
    cols_label(
      race_eth = "Race",
      Dem = "DEM.",
      Rep = "REP.",
      Und = "UND.") %>%
    fmt_percent(columns = vars(Dem, Rep, Und),
                decimals = 0)
## we use the fmt_percent function in order to turn our proportions into percents
## we use the tab_header function in order to put more labels on the plot
```


```{r, echo=FALSE}
orig %>%
  select(educ, final_weight) %>%
  filter(educ != "[DO NOT READ] Refused") %>%
  mutate(educ = fct_relevel(educ, c("Grade school", "High school", "Some college or trade school", "Bachelors' degree", "Graduate or Professional Degree"))) %>%
  ## We use the fct_relevel function to re order the different levels of educ to 
  ## match the plot we were given to replicate
  ggplot(aes(x = educ, y = final_weight)) +
  geom_violin() +
  coord_flip() +
  ## we use coord_flip here to switch the x and the y 
  geom_jitter(size = 1, alpha = .5, height = 0) +
  ## we use the alpha, size and height to mutate the look of the points plotted 
  labs(
    title = "More Educated Matter Less in North Carolina 9th",
    subtitle = "Poll gives more weight to people who are less likely to participate in polls",
    caption = "New York Times Upshot/Siena College 2018 live polls") +
ylab("Weight Given to Respondent in Calculating Poll Results") +
xlab(" ")
## we use the labs function here to label our plot 
## we use the xlab function with " " within it to keep the axis clear of a label 


```
```{r, echo=FALSE}
orig%>%
   group_by(race_eth,response)%>%
  filter(response != '3')%>%
   filter(race_eth != "[DO NOT READ] Don't know/Refused")%>%
  summarize(N = n())%>%
  ggplot(aes(x = race_eth, y = N, color = response, fill = response)) +
  geom_col(position = "dodge2") +
  ggtitle("Response looked at by Race")+
    labs(x = "Race",y = "Party Response") +
    theme(legend.position = "top")

## Here I grouped by race_eth and response
## I filtered out those who didn't know or wouldn't
## record their race.  I then filtered out those who responded "3." I then preforme ## a bar graph with the postion "dodge2" in order to place the bars indicating race ## and party response side by side. I wanted to create this plot in order to 
## understand better and look into if there are any themes between race and party ## response within the ## dataset. 
